---
title: "Portfoliomanagement and Financial Analysis - Assignment 1"
subtitle: "Submit until Monday 2020-09-21, 13:00"
author: "Baumann, Nicolas"
output: html_notebook
---

# Packaged Load 
```{r load_packs}
pacman::p_load(tidyverse,
               tidyquant,
               FFdownload,
               timeDate,
               timetk,
               xts,
               magrittr,
               tidyr)
```

For all exercises please refer to my book [Tidy Portfoliomanagement in R](https://bookdown.org/sstoeckl/Tidy_Portfoliomanagement_in_R). Unfortunately some functions (e.g. `get_exchange()`) are not working on rstudio.cloud, so please try to solve the exercises without. Also remember, that ecverything you do below must be **explained** to me (why? what does this mean? what is the interpretation?). If you have any questions or problems, please refer to the assignment forum on moodle.

# Exercise 1: xts

## Task
Create a daily time series for `r lubridate::year(Sys.time())`:

1. Find the subset of first and last days per month/quarter (uniquely)
2. Take December `r lubridate::year(Sys.time())-1` and remove all weekends and holidays in Zurich (Tokyo)
3. create a series of five dates & times in New York. Show them for New York, London and Belgrade

## Nessecairy Theorie
NONE

```{r}
# Exercise 1.1

## Creation of Time Dates Variant Nr 1
dates1 <- seq(as.Date("2020-01-01"), length=365, by="day"); dates1
dates2 <- seq(as.Date("2020-01-01"), length=12, by="month"); dates2

## Creation of Time Dates Variant Nr 2
dates <- timeSequence(from = "2020-01-01", to = Sys.time(), by = "day")

## Task
first_day_in_month    <- timeFirstDayInMonth(dates2);first_day_in_month
last_day_in_month     <- timeLastDayInMonth(dates2);last_day_in_month 
first_day_in_quarter  <- timeFirstDayInQuarter(dates2);first_day_in_quarter 
last_day_in_quarter   <- timeLastDayInQuarter(dates2);last_day_in_quarter
```

```{r}
# Exercise 1.2
dates3 <- timeSequence(from = "2019-12-01", to = Sys.time() , by = "day"); dates3

# Select only weekdsay
dates_isWeekday <- dates3[isWeekday(dates3)]; dates_isWeekday 

# Check for weekdays
dayOfWeek(dates_isWeekday) 

# Select only BusinessDays of Zurich
dates_isBusinessDays_ZH <- dates3[isBizday(dates3, holidayZURICH(2019))]; dates_isBusinessDays_ZH 

dayOfWeek(dates_isBusinessDays_ZH)


```

```{r}
# Exercise 1.2
D_T_NY2 <- timeSequence(from = "2019-12-01", to = Sys.time(), by = "min", length.out = 5); D_T_NY2
# or 
D_T_NY <- seq(as.timeDate(as.POSIXct("2009-01-05 14:19:12", format="%Y-%m-%d %H:%M:%S", tz="UTC")), length=5, by="day"); D_T_NY


timeDate(D_T_NY2, zone = "NewYork", FinCenter = "Tokyo")

timeDate(D_T_NY2, zone = "NewYork", FinCenter = "London")

timeDate(D_T_NY2, zone = "NewYork", FinCenter = "Belgrade")
```

# Exercise 2: Download Financial Data and Merge

1) Download information on all stocks currently part of the S&P500. 
2) Select 10 that have data back to 2000. 
3) Additionally download the S&P 500 index and the four Fama-French factors including the risk-free rate (using my package [`ffdownload`](https://github.com/sstoeckl/ffdownload)). 
4) Merge all data together and calculate returns (simple or continuous returns?).
5) Split your data in two files: One holding daily returns and one with monthly returns. 
6) Additionally show how to we could get from long to wide format to transfer between `tibble` (`tsibble`) and xts.


```{r}
# 1) Download information on all stocks currently part of the S&P500. 

## Some commands for getting an overview about available:

### 1. exchanges - Get the list of stock exchange options
tq_exchange_options()

### 2. indices - Get the list of stock index options
tq_index_options() 

### 3. data sources  
tq_get_options()

### 4. Get all stocks in a stock-exchange
tq_exchange("NASDAQ")


# Information on S&P500 V1
sp500 <- tq_index("SP500")
sp500

# Getting an overview about all information on all stocks currently part of the S&P500!
glimpse(sp500)

# To have 10 stocks that have data back to 2000, we look at the exchange NYSE, 
# where we have the information about the IPO Year (variables "ipo.year")
nyse <- tq_exchange("NYSE") 
glimpse(nyse)
# We have now an overview about all ipo years on all stocks currently at the NYSE!

```

```{r}
# 2) Select 10 that have data back to 2000 and SP500

#Selection of 10 that have data back to 2000 and calculation of the daily return
startDate <- "2000-09-01"
stockSelection <- c('T', 'WMT', 'MSFT', 'BAC', 'PG', 'MCD', 'JPM', 'LIN', 'VZ', 'INTC')

# First with daily values
stockSelectionDaily <- stockSelection %>%
  tq_get(get = "stock.prices", 
         from = startDate, 
         to = TODAY()) %>%
  group_by(symbol) %>% #Group columns by the same value
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "daily", 
               col_rename = 'return') #Calculation of the daily return

#Selection of the SP500 and calculation of the daily return
sp500Daily <- tq_get("^GSPC", 
                     get = "stock.prices", 
                     from = startDate, to = TODAY()) %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "daily", 
               col_rename = 'SP500') #Calculation of daily returns from index

# The same but with monthly dates
stockSelectionMonthly <- stockSelection %>%
 tq_get(get = "stock.prices", 
        from = startDate, 
        to = TODAY()) %>%
  group_by(symbol) %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "monthly", 
               col_rename = 'return')

sp500Monthly <- tq_get("^GSPC", 
                       get = "stock.prices", 
                       from = startDate, 
                       to = TODAY()) %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "monthly", 
               col_rename = 'SP500')

# Preparing the data and merging it
stockSelectionDaily_cols <- stockSelectionDaily %>% 
  spread(symbol, return) #a column with the returns is created for the companies

stockSelectionMonthly_cols <- stockSelectionMonthly %>% 
  spread(symbol, return)

# stockSelectionDaily_xts <- tk_xts(stockSelectionDaily_cols, date_var = date)

dataDaily <- stockSelectionDaily_cols %>% 
  merge(sp500Daily, by = "date") #where the dates are the same, they are in the same line (only if there is an entry for both)

dataMonthly <- stockSelectionMonthly_cols %>% 
  merge(sp500Monthly, by = "date")
```

```{r}

# 3) Additionally download the four Fama-French factors including the risk-free rate (using my package [`ffdownload`](https://github.com/sstoeckl/ffdownload)).


#Downloading the datasets from Kenneth French's Website.
tmpf <- tempfile(fileext = ".RData") 
tmpd <- tempdir()
tmptxt <- tempfile(fileext = ".txt")
inputlist <- c("F-F_Research_Data_Factors","F-F_Momentum_Factor","F-F_ST_Reversal_Factor","F-F_LT_Reversal_Factor")
# Now process only these files if they can be matched (download only)
FFdownload(output_file = tmpf,      # name of the .RData file to be saved (include path if necessary)
           tempdir = tmpd,          #	specify if you want to keep downloaded files somewhere save.
           exclude_daily = FALSE,   # excludes the daily datasets (are not downloaded) ==> speeds the process up considerably
           download = TRUE,         # TRUE if you actually want to download again. FALSE (specify tempdir) to keep processing the already downloaded files
           download_only = FALSE,   # FALSE if you want to process all your downloaded files (inputlist!) at once
           listsave=tmptxt,         # the list of unzipped files is saved here
           inputlist=inputlist)     # if not NULL, FFdownload tries to match the names from the list with the list of zip-files
load(tmpf)
list.files(tmpd)

# Prepare Fama-French data and merge it 

## Daily!! -> timeseries converted from Fama French to tibble
ffFactorsDaily <- tk_tbl(FFdownload$`x_F-F_Research_Data_Factors`$daily$Temp2, 
                         timetk_idx = TRUE, 
                         rename_index = "date") 

### Selection for the relevant data, which are greater or equal the start date
ffFactorsDaily <- ffFactorsDaily[ffFactorsDaily$date >= startDate,,,,] 

#### The last data will be output #Fama-French data is only available until 30.06.2020 as of today
tail(ffFactorsDaily) 

# Merge the Data with the Daily Data from before
dataDaily <- dataDaily %>% 
  merge(ffFactorsDaily, 
        by = "date")

# Same for monthly -> timeseries converted from Fama French to tibble
ffFactorsMonthly <- tk_tbl(FFdownload$`x_F-F_Research_Data_Factors`$monthly$Temp2, 
                           timetk_idx = TRUE, 
                           rename_index = "date")%>%
  mutate(date=as.Date(date, 
                      frac=1))

### Selection for the relevant data, which are greater or equal the start date
ffFactorsMonthly <- ffFactorsMonthly[ffFactorsMonthly$date >= startDate,,,,]

#### The last data will be output #Fama-French data is only available until 30.06.2020 as of today
tail(ffFactorsMonthly)

# Merge the Data with the Monthly Data from before
dataMonthly <- dataMonthly %>% 
  merge(ffFactorsMonthly, 
        by = "date")

# Export work into csv
write.table(dataDaily , file = "./dataDaily.csv")
write.table(dataMonthly, file = "./dataMonthly.csv")

# Transform tibble into time series

dailyTimeSeries <- xts(dataDaily[,-1], order.by = dataDaily[,1])
monthlyTimeSeries <- xts(dataMonthly[,-1], order.by = dataMonthly[,1]) 
#[row,column] -1=without first column , = we want all rows



```
```{r}
#10 S&P 500 stocks with IPO<2000

SP <- tq_index("SP500")
NASDAQ <- tq_exchange("NASDAQ")
NYSE <- tq_exchange("NYSE")

 
stocks.selection <- SP %>% 
inner_join(rbind(NYSE,NASDAQ) %>% 
             select(symbol,
                    last.sale.price,
                    market.cap,
                    ipo.year),
           by=c("symbol")) %>% # join datasets
  filter(ipo.year<2000&!is.na(market.cap)) %>% # filter years with ipo<2000 or ipo=NA
  arrange(desc(weight)) %>% # sort in descending order
  slice(1:10)

  
# Additional Data for the S&P500-index

stocks.prices <- stocks.selection$symbol %>%  # daily prices
    tq_get(get  = "stock.prices",
           from = "2000-01-01",
           to = "2019-12-31") %>%
    group_by(symbol)

    
index.prices <- "^GSPC" %>% 
  tq_get(get  = "stock.prices",
         from = "2000-01-01",
         to = "2019-12-31") 
stocks.prices %>% 
  slice(1:2) # show the first two entries of each group

# Dividends and Stock Splits
stocks.dividends <- stocks.selection$symbol %>% 
    tq_get(get  = "dividends",
           from = "2000-01-01",
           to = "2019-12-31") %>%
    group_by(symbol)
    
stocks.splits <- stocks.selection$symbol %>% 
    tq_get(get  = "splits",
           from = "2000-01-01",
           to = "2019-12-31") %>%
    group_by(symbol)

#Stock Ratios does not work
stocks.ratios <- stocks.selection$symbol %>% 
    tq_get(get  = "key.ratios",from = "2000-01-01",to = "2019-12-31") %>%
    group_by(symbol)

# Fama-French Data
factors <- FFdownload$`x_F-F_Research_Data_Factors`$monthly$Temp2 %>% 
          tk_tbl(rename_index="date") %>% # make tibble
          mutate(date=as.Date(date, frac=1)) %>% # make proper month-end date format
          gather(key=FFvar,value = price,-date) # gather into tidy format

factors %>% group_by(FFvar) %>% slice(1:2)

#Stock prices monthly
stocks.prices.monthly <- stocks.prices %>% 
                  tq_transmute(select = c(adjusted,volume), # which column to choose
                               mutate_fun = to.monthly,     # funtion: make monthly series
                               indexAt = "lastof") %>%      
                  ungroup() %>% mutate(date=as.yearmon(date)) 

# Stock Returns monthly
stocks.returns <- stocks.prices %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,   # create monthly  returns
               period="monthly",
               type="arithmetic") %>%
  ungroup() %>% 
  mutate(date=as.yearmon(date))

save(stocks.returns,file="stocksreturn_monthly.RData")

# Stocks Return Daily
stocks.returns.daily <- stocks.prices %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,   # create daily  returns
               period="daily",
               type="arithmetic") %>% 
  ungroup() %>% 
  mutate(date=as.yearmon(date))
                  
save(stocks.returns.daily,file="stocksreturns_daily.RData")                  
  
# Index Returns monthly                  
index.returns <- index.prices %>% 
  tq_transmute(select = adjusted,mutate_fun = periodReturn,
               period="monthly", 
               type="arithmetic") %>%
  mutate(date=as.yearmon(date))
                  
# Factor Returns monthly (already)
factors.returns <- factors %>% 
  mutate(price=price/100) %>%
  mutate(date=as.yearmon(date)) 

# Show first 5 enteries
stocks.prices.monthly %>% 
  ungroup() %>% 
  slice(1:5) 

stocks.returns %>% 
  ungroup() %>% 
  slice(1:5)

index.returns %>% 
  ungroup() %>% 
  slice(1:5) 

factors.returns %>% 
  ungroup() %>% 
  slice(1:5)

# Merging data together
first.merge <- merge(stocks.prices.monthly,
                     stocks.returns, 
                     by = c("symbol","date"))

stocks.final <- merge(merge(first.merge,index.returns, 
                            by = "date"),
                      factors.returns, by= "date")

stocks.returns.daily
stocks.returns
```



# Exercise 3: Plotting Data

Carefully work through `vignette("TQ04-charting-with-tidyquant")` and create plots using [ggplot](https://ggplot2.tidyverse.org/) from the tidyverse. 

1) Select four assets to highlight all functions that are important for you!

```{r}

# Exercise 3: Plotting Data
 
# 1) Select four assets 
getSymbols(Symbols = "AMZN", from="2006-01-01", to=Sys.time(), periodicity="monthly")
getSymbols(Symbols = "AAPL", from="2006-01-01", to=Sys.time(), periodicity="monthly")
getSymbols(Symbols = "MSFT", from="2006-01-01", to=Sys.time(), periodicity="monthly")
getSymbols(Symbols = "GOOG", from="2006-01-01", to=Sys.time(), periodicity="monthly")

stocks <- as.xts(data.frame(AAPL = AAPL[, "AAPL.Close"], 
                            AMZN = AMZN[, "AMZN.Close"],
                            MSFT = MSFT[, "MSFT.Close"], 
                            GOOG = GOOG[, "GOOG.Close"]))
head(stocks)

# plotting the data
plot(as.zoo(stocks), screens = 1, lty = 1:4, xlab = "Date", ylab = "Price")
legend("right", c("AAPL", "AMZN", "MSFT", "GOOG"), lty = 1:4, cex = 0.5)


vecst<-data.matrix(as.data.frame(stocks)) #convert xts into matrix

boxplot(vecst) #boxplot of matrix

h<-hist(vecst, breaks=10, col="red", xlab="ClosingPrice",
   main="Histogram with Normal Curve")
   xfit<-seq(min(vecst),max(vecst),length=40)
yfit<-dnorm(xfit,mean=mean(vecst),sd=sd(vecst))
yfit <- yfit*diff(h$mids[1:2])*length(vecst)
lines(xfit, yfit, col="blue", lwd=2)

qqnorm(stocks)

```

```{r}

#Get AAPL, AMZN, NFLX, FB STock Prices

AAPL <- tq_get("AAPL", get = "stock.prices", from = "2015-01-01", to = "2019-12-31")

AMZN <- tq_get("AMZN", get = "stock.prices", from = "2015-01-01", to = "2019-12-31")

NFLX <- tq_get("NFLX", get = "stock.prices", from = "2015-01-01", to = "2019-12-31")

FB <- tq_get("FB", get = "stock.prices", from = "2015-01-01", to = "2019-12-31")


# boxplot of matrix
boxplot(vecst) 


h<-hist(vecst, breaks=10, col="red", xlab="ClosingPrice",
   main="Histogram with Normal Curve")
   xfit<-seq(min(vecst),max(vecst),length=40)
yfit<-dnorm(xfit,mean=mean(vecst),sd=sd(vecst))
yfit <- yfit*diff(h$mids[1:2])*length(vecst)
lines(xfit, yfit, col="blue", lwd=2)

qqnorm(stocks)

# Histogram (incl. normal density)

hist(AAPL$adjusted, # histogram APPLE
 col="violet", # column color
prob = TRUE, # show densities instead of frequencies
 xlab = "Adjusted",
 main = "APPLE")
lines(density(AAPL$adjusted), # density plot
 lwd = 2, # thickness of line
 col = "pink")

hist(AMZN$adjusted, # histogram AMAZON
 col="peachpuff", # column color
prob = TRUE, # show densities instead of frequencies
 xlab = "Adjusted",
 main = "AMAZON")
lines(density(AMZN$adjusted), # density plot
 lwd = 2, # thickness of line
 col = "chocolate3")

hist(NFLX$adjusted, # histogram NETFLIX
 col="lightpink", # column color
prob = TRUE, # show densities instead of frequencies
 xlab = "Adjusted",
 main = "NETFLIX")
lines(density(NFLX$adjusted), # density plot
 lwd = 2, # thickness of line
 col = "cyan4")
 
 hist(FB$adjusted, # histogram FACEBOOK
 col="rosybrown1", # column color
prob = TRUE, # show densities instead of frequencies
 xlab = "Adjusted",
 main = "FACEBOOK")
lines(density(FB$adjusted), # density plot
 lwd = 2, # thickness of line
 col = "royalblue1")

#Box-Plot
boxplot(AAPL$adjusted, main="APPLE", xlab="Adjusted",col="lightsteelblue1", horizontal = TRUE)

boxplot(AMZN$adjusted, main="AMAZON", xlab="Adjusted",col="yellow", horizontal = TRUE)

boxplot(NFLX$adjusted, main="NETFLIX", xlab="Adjusted",col="red", horizontal = TRUE)

boxplot(FB$adjusted, main="FACEBOOK", xlab="Adjusted",col="royalblue3", horizontal = TRUE)

#gg-Plot

qqnorm(AAPL$adjusted)
qqline(AAPL$adjusted,col="royalblue",lwd=3) #to see if normal distribution

qqnorm(AMZN$adjusted)
qqline(AMZN$adjusted,col="yellow",lwd=3)

qqnorm(NFLX$adjusted)
qqline(NFLX$adjusted,col="red",lwd=3)

qqnorm(FB$adjusted)
qqline(FB$adjusted,col="blue",lwd=3)

```


# Exercise 4: Statistics

Here you might use all `tidyquant`-vignettes! My shiny-script here might also help you to get an idea: [www.riskindex.eu:3838/mci](www.riskindex.eu:3838/mci).

### Exercise 4.1 Within securities

For the four securities calculate all interesting statistics (measures of location, dispersion, skewness and kurtosis). Check returns for univariate (and multivariate) normality.



```{r}
Stocks.raw <- c("MSFT","AAPL","AMZN","GOOG") %>%
    tq_get(get  = "stock.prices", from = "2000-01-01", to   = Sys.Date()) %>%
    group_by(symbol)
Stocks_ret_daily <- Stocks.raw %>%
    tq_transmute(select = adjusted, mutate_fun = periodReturn,
                 period = "daily", col_rename = "return", type="log")
Stocks_ret_monthly <- Stocks.raw %>%
    tq_transmute(select = adjusted, mutate_fun = periodReturn,
                 period = "monthly", col_rename = "return", type="log")

#geometric and arithmetic mean

#monthly 

Stocks_ret_monthly %>% summarize(geometric_mean=mean.geometric(return), arithmetic_mean=mean(return)) %>%
          mutate_at(-1, round, 5) %>% t()


#daily
Stocks_ret_daily %>% summarize(geometric_mean=mean.geometric(return), arithmetic_mean=mean(return)) %>%
          mutate_at(-1, round, 5) %>% t()


#Skewness and kurtosis

Stocks_ret_daily %>% summarize(Skewness=skewness(return), "Ex. Kurtosis"=kurtosis(return)) %>%
          mutate_at(-1, round, 3) %>% t()


#measures of spread
#monthly
Stocks_ret_monthly %>% summarize(Volatility=sd(return), Range=max(return)-min(return), IQR=IQR(return)) %>%
          mutate_at(-1, round, 3) %>% t()

#daily 
Stocks_ret_daily %>% summarize(Volatility=sd(return), Range=max(return)-min(return), IQR=IQR(return)) %>%
          mutate_at(-1, round, 3) %>% t()

#Standard deviation - measures of spread financial risk

#monthly
Stocks_ret_monthly %>% summarize(Semideviation=SemiDeviation(return), 
  "VaR(0.05)"=VaR(return,p=0.05), "CVaR(0.05)"=CVaR(return,p=0.05)) %>%
  mutate_at(-1, round, 3) %>% t()
  
#daily
Stocks_ret_daily %>% summarize(Semideviation=SemiDeviation(return), 
  "VaR(0.05)"=VaR(return,p=0.05), "CVaR(0.05)"=CVaR(return,p=0.05)) %>%
  mutate_at(-1, round, 3) %>% t()




```
### Exercise 4.2 Between securities and with index

Plot all securities vis-a-vis the index. Include a regression line and regression information. Can you plot rolling correlations between assets (and/or the index)?
```{r}
#grouping the 4 securities, getting monthly returns
Ra<-c("AAPL","AMZN","MSFT","GOOG")%>%
tq_get(get="stock.prices",from="2016-12-31",to="2019-12-31")%>%
group_by(symbol)%>%
tq_transmute(select     = adjusted, mutate_fun = periodReturn,period     = "monthly",col_rename = "Ra")

#monthly Returns for the Dow Jones
Rb <- c("DJI") %>%
    tq_get(get  = "stock.prices",from="2016-12-31",to="2019-12-31")  %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "monthly",
                 col_rename = "Rb")
RaRb <- left_join(Ra, Rb, by = c("date" = "date"))

RaRb %>%
    tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)

#AAPL vs Dow Jones    
stock_prices <- c("DJI", "AAPL") %>%
    tq_get(get  = "stock.prices",
         from="2016-12-31",to="2019-12-31") %>%
    group_by(symbol)

stock_pairs <- stock_prices %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "daily",
                # type       = "log",
                 col_rename = "returns") %>%
    spread(key = symbol, value = returns)
    
stock_pairs %>%
  ggplot(aes(x = DJI, y = AAPL)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    geom_smooth(method = "lm") +
    labs(title = "Returns Relationship of Apple and Dow Jones 2016/12/31 to 2019/12/31 - Method: lm") +
    theme_tq()

#AMZN vs Dow Jones
stock_prices <- c("DJI", "AMZN") %>%
    tq_get(get  = "stock.prices",
         from="2016-12-31",to="2019-12-31") %>%
    group_by(symbol)

stock_pairs <- stock_prices %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "daily",
                # type       = "log",
                 col_rename = "returns") %>%
    spread(key = symbol, value = returns)

stock_pairs %>%
    ggplot(aes(x = DJI, y = AMZN)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    geom_smooth(method = "lm") +
    labs(title = "Returns Relationship of Amazon and Dow Jones 2016/12/31 to 2019/12/31 - Method: lm") +
    theme_tq()
    
#MSFT vs Dow Jones
stock_prices <- c("DJI", "MSFT") %>%
    tq_get(get  = "stock.prices",
         from="2016-12-31",to="2019-12-31") %>%
    group_by(symbol)

stock_pairs <- stock_prices %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "daily",
                # type       = "log",
                 col_rename = "returns") %>%
    spread(key = symbol, value = returns)

stock_pairs %>%
    ggplot(aes(x = DJI, y = MSFT)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    geom_smooth(method = "lm") +
    labs(title = "Returns Relationship of Microsoft and Dow Jones 2016/12/31 to 2019/12/31 - Method: lm") +
    theme_tq()
    
#Google vs Dow Jones

stock_prices <- c("DJI", "GOOG") %>%
    tq_get(get  = "stock.prices",
         from="2016-12-31",to="2019-12-31") %>%
    group_by(symbol)

stock_pairs <- stock_prices %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "daily",
                # type       = "log",
                 col_rename = "returns") %>%
    spread(key = symbol, value = returns)

stock_pairs %>%
    ggplot(aes(x = DJI, y = GOOG)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    geom_smooth(method = "lm") +
    labs(title = "Returns Relationship of Google and Dow Jones 2016/12/31 to 2019/12/31 - Method: lm") +
    theme_tq()


#Can you plot rolling correlations between assets (and/or the index)?
Ra <- c("AAPL", "GOOG", "MSFT","AMZN") %>%
    tq_get(get  = "stock.prices",
          from = "2013-12-31",
           to   = "2018-12-31") %>% 
    group_by(symbol) %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "monthly",
                  type       = "log",
                 col_rename = "Ra")

Rb <- c("DJI") %>%
    tq_get(get  = "stock.prices",
           from = "2013-12-31",
           to   = "2018-12-31") %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "monthly",
                  type       = "log",
                 col_rename = "Rb")

RaRb <- left_join(Ra, Rb, by = c("date" = "date"))

rolling_corr <- RaRb %>%
    tq_transmute_xy(x          = Ra,
                    y          = Rb,
                    mutate_fun = runCor,
                    n          = 6,
                    col_rename = "rolling.corr.6")

rolling_corr %>%
    ggplot(aes(x = date, y = rolling.corr.6, color = symbol)) +
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    geom_line(size = 1) +
    labs(title = "Six Month Rolling Correlations to Dow Jones (2013/12/31 to 2018/12/31)",
         x = "", y = "Correlation", color = "") +
    facet_wrap(~ symbol, ncol = 2) +theme_tq() +
    scale_color_tq()


```

```{r}
table.CAPM
```

## Exercise 5: Performance Analysis

Create multiple portfolios using `tq_portfolio()` (e.g. an equally weighted one, a market-value weighted one, and one where you create a trading strategy according to your liking). DO a performance analysis a la `vignette("TQ05-performance-analysis-with-tidyquant")`.

To make a portfolio I have to choose assets. Therefore I took the monthly stock prices from Apple, Google, Netflix and Amazon from 31.12.2013 to 31.12.2019.

```{r}
stock_returns_monthly <- c("AAPL", "GOOG", "NFLX", "AMZN") %>%
  tq_get(get  = "stock.prices",
         from = "2013-12-31",
         to   = "2019-12-31") %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "monthly", 
               col_rename = "Ra")
```

# Creating a repetition for three portfolios
```{r}
stock_returns_monthly_multi <- stock_returns_monthly %>%
  tq_repeat_df(n = 3)
```

# Market-value weighted Portfolio, Using the market values as of 13th September 2019
```{r}
MV_AAPL<-988.57
MV_GOOG<-859.51
MV_NFLX<-128.79
MV_AMZN<-909.84
MV_sum<-MV_NFLX+MV_AAPL+MV_AMZN+MV_GOOG
```

#Now I create the vector for the equally weighted one (25% for each stock). 
One portfolio is equally weighted with 25% and the 3rd portfolio is weighted after my preferences

```{r}
weights <- c(
  0.25, 0.25, 0.25, 0.25, 
  MV_AAPL/MV_sum, MV_GOOG/MV_sum, MV_NFLX/MV_sum, MV_AMZN/MV_sum, 
  0.2, 0.4, 0.2, 0.2)
```

#To measure the performance of the 3 portfolios I choose the SP500 as baseline returns
```{r}
baseline_returns_monthly <- "^GSPC" %>%
  tq_get(get  = "stock.prices",
         from = "2013-12-31",
         to   = "2019-12-31") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "monthly", 
               col_rename = "Rb")
```
 

#The next step is to create the portfolios according to the weight table
```{r}
stocks <- c("AAPL", "GOOG", "NFLX", "AMZN")
weights_table <-  tibble(stocks) %>%
  tq_repeat_df(n = 3) %>%
  bind_cols(tibble(weights)) %>%
  group_by(portfolio)
```

```{r}
weights_table
```
#Creating the returns for the portfolios
```{r}
portfolio_returns_monthly_multi <- stock_returns_monthly_multi %>%
  tq_portfolio(assets_col  = symbol, 
               returns_col = Ra, 
               weights     = weights_table, 
               col_rename  = "Ra")
portfolio_returns_monthly_multi
```
#Combining the portfolios with the baseline
```{r}
RaRb_multiple_portfolio <- left_join(portfolio_returns_monthly_multi, 
                                     baseline_returns_monthly,
                                     by = "date")
```                                     
#A performance analysis can be done now --> CAPM table is to be created
```{r}
RaRb_multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)
```  
# Sharpe Ratio Table
```{r}
RaRb_multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = NULL, performance_fun = SharpeRatio)
```
# Table Stats
```{r}
RaRb_multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = NULL, performance_fun = table.Stats)
```